\documentclass[a4paper, 12pt]{article}

\usepackage{geometry}
\geometry{
	margin=1cm,
	a4paper
}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}
\usepackage{multicol}
\usepackage{enumitem}

\newtcolorbox{question}[2][Title]{
	colback=blue!10,
	fonttitle=\Large\bfseries,
	title={#2},
	height=10cm,
	boxrule=3pt,
	fontupper=\large,
	left=1cm,
	right=1cm,
	top=0.6cm,
	toptitle=0.2cm,
	bottomtitle=0.2cm,
	#1
}

\begin{document}
	\pagestyle{empty}
	\begin{question}[colback=red!10]{Flexible or not?}
  		Order the following materials from \textbf{most flexible} to \textbf{least}
  		
  		\begin{enumerate}[font=\bfseries]
  		\centering
  			\item Paper
  			\item Glass
  			\item Metal
  			\item Rubber
  		\end{enumerate}
	\end{question}
	\begin{question}[]{True or False?}
  		Which sentences are \textbf{correct}?
  		
  		\begin{multicols}{2}
  		\begin{enumerate}[font=\bfseries]
  			\item Glass is made from sand.
  			\item All metals are magnetic.
  			\item Steel is harder than diamond.
  			\item Pencils and diamond are made from the same material.
  			\item Spider silk is one of the strongest materials in the world.
  			\item Metals can be used in the human body.
  			\item Metals are transparent.
  			\item Plastics are made from oil.
  			\item You can melt wood.
  			\item Steel doesn’t float.
  		\end{enumerate}
  		\end{multicols}
	\end{question}
	\newpage
	\begin{question}[colback=green!10]{Higher or lower?}
  		Is the melting point of ...... \textbf{higher} or \textbf{lower} than aluminium?
  		\begin{enumerate}
  		\centering
  			\item Titanium
  			\item Steel
  			\item Ice
  			\item Glass
  		\end{enumerate}
	\end{question}
	\begin{question}[colback=cyan!10]{Biodegradable?}
  		How long would a plastic bottle take to decompose?
  		\begin{itemize}
  		\centering
  			\item 1 year
  			\item 10 years
  			\item 250 years
  			\item 450 years
  		\end{itemize}
	\end{question}
	\newpage
	\begin{question}[]{Transparent?}
		Which material is transparent, allowing light to go through it easily?
		\begin{itemize}
  		\centering
  			\item Metal
  			\item Wood
  			\item Glass
  			\item Plastic
  		\end{itemize}
	\end{question}
	\begin{question}[colback=orange!10]{When were they discovered?}
		Can you order these materials by the year that they were discovered?
		\begin{enumerate}
  		\centering
  			\item Graphene % 2000s
  			\item Steel % many many years ago lol
  			\item Man-made plastic % early 1900s, bakelite
  			\item Structure of DNA % mid 1900s
  		\end{enumerate}
	\end{question}
\end{document}








